News Story

### 2023-04-11 censusmap.qmd
4th

# Download census data
tx_census <- get_acs(
  geography = "county",
  variables = "B15003_022",
  state = "TX",
  survey = "acs5",
  year = 2019)

@@

tm_shape(tx_map_data) +
  tm_polygons(variables = "B15003_022",
              col = "grey", 
              border.col = "black",
              style = "quantile",
              palette = "Blues",
              title = "Percentage of Individuals with more than 25 with Bachelor's Degree or Higher") +
  tm_layout(main.title = "Texas Counties",
            legend.outside = TRUE)

>>>>

# Download census data
tx_census <- get_acs(
  geography = "county",
  variables = "B15003_022",
  state = "TX",
  survey = "acs5",
  year = 2019,
  geometry = TRUE)

@@

tm_shape(tx_census) +
  tm_polygons("estimate",
              border.col = "black",
              style = "quantile",
              palette = "Blues",
              title = "Percentage of Individuals with more than 25 with Bachelor's Degree or Higher") +
  tm_layout(main.title = "Texas Counties",
            legend.outside = TRUE)

### 2023-04-11 newsstory.qmd
3rd commit
4th

---
title: "News Story"
---

@@

**Burberry: the brand\'s dilemma with sustainability**

@@

With the influx of these concerned consumers, brands must adjust their strategies and undertake the topic of sustainability to stay competitive. For example, in the luxury fashion industry, fur has always been an important medium. In recent years, there has been a decrease in demand for the luxurious animal by product because there is a heightened awareness of the detrimental effects of the fur industry. For that reason, some designers are beginning to swap fur for something faux. In my opinion, this shift is beneficial and will have a positive impact on a luxury brand\'s reputation.\

One high end brand that is highly invested in sustainability is Burberry, the British fashion house created in 1865 by Thomas Burberry. The company proved to be unique in the high fashion market when Thomas created Gabardine, a \'breathable, weatherproof and hardwearing fabric revolutionising rainwear\'. Also adding to the originality of the brand is Thomas Burberry\'s creation of the iconic pattern-based scarves, purses, and trench coats. In 2017, when the company\'s annual report was released, environmental activists protested the brand because it had burned almost \$29 million dollars of unsold inventory in a year. With the major repercussion of the brand\'s lack of sustainability commitment, social media backlash, the movement #Burnberry arose to demand change. The protests proved to be effective since Burberry is now dedicated to improving sustainability inside the company.\

As of now, the brand uses 58% of its energy and 68% of its electricity from clean energy sources and Burberry plans to stay committed to sustainability in the future. The brand has made several promises to become more sustainable for 2022. For instance, Burberry has committed to stopping the use of real fur and burning unwanted items, become carbon neutral by 2022, and operate entirely by renewable energy. In addition, Burberry has released a \'Responsibility Agenda\' to set goals for increasing sustainability within the company. The agenda focuses on three areas: product, company, and communities. Each area is centered on achieving progress by making the brand\'s product more recyclable, ridding the practice of burning unsaleable products, and impacting teachers and students by increasing mentoring programs in developing regions.\

The \'Responsibility Agenda\' goals abides with the Paris Climate Agreement and the UN\'s 17 Sustainable Development Goals. Burberry committed to becoming a 100% renewable energy run company, and to create a Manufacturing Excellence Program focused on enhancing worker wellbeing in the company\'s supply chain. The brand has been recognized with two awards for its sustainable fashion approach: Leading luxury brand in the 'Textiles, Apparel & Luxury Goods' sector by the DJSI 2018, and \'Bronze Class\' in RobecoSAM\'s 2018 Sustainability Yearbook.\

>>>>

---
title: "News Story"
author: "Giovanna Lino"
---

@@

**Burberry: the brand's dilemma with sustainability**

@@

With the influx of these concerned consumers, brands must adjust their strategies and undertake the topic of sustainability to stay competitive. For example, in the luxury fashion industry, fur has always been an important medium. In recent years, there has been a decrease in demand for the luxurious animal by product because there is a heightened awareness of the detrimental effects of the fur industry. For that reason, some designers are beginning to swap fur for something faux. In my opinion, this shift is beneficial and will have a positive impact on a luxury brand's reputation.\

One high end brand that is highly invested in sustainability is Burberry, the British fashion house created in 1865 by Thomas Burberry. The company proved to be unique in the high fashion market when Thomas created Gabardine, a 'breathable, weatherproof and hardwearing fabric revolutionising rainwear'. Also adding to the originality of the brand is Thomas Burberry's creation of the iconic pattern-based scarves, purses, and trench coats. In 2017, when the company's annual report was released, environmental activists protested the brand because it had burned almost \$29 million dollars of unsold inventory in a year. With the major repercussion of the brand's lack of sustainability commitment, social media backlash, the movement #Burnberry arose to demand change. The protests proved to be effective since Burberry is now dedicated to improving sustainability inside the company.\

As of now, the brand uses 58% of its energy and 68% of its electricity from clean energy sources and Burberry plans to stay committed to sustainability in the future. The brand has made several promises to become more sustainable for 2022. For instance, Burberry has committed to stopping the use of real fur and burning unwanted items, become carbon neutral by 2022, and operate entirely by renewable energy. In addition, Burberry has released a 'Responsibility Agenda' to set goals for increasing sustainability within the company. The agenda focuses on three areas: product, company, and communities. Each area is centered on achieving progress by making the brand's product more recyclable, ridding the practice of burning unsaleable products, and impacting teachers and students by increasing mentoring programs in developing regions.\

The 'Responsibility Agenda' goals abides with the Paris Climate Agreement and the UN's 17 Sustainable Development Goals. Burberry committed to becoming a 100% renewable energy run company, and to create a Manufacturing Excellence Program focused on enhancing worker wellbeing in the company's supply chain. The brand has been recognized with two awards for its sustainable fashion approach: Leading luxury brand in the 'Textiles, Apparel & Luxury Goods' sector by the DJSI 2018, and 'Bronze Class' in RobecoSAM's 2018 Sustainability Yearbook.\
